\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
fixes in the graph processing section, and added wordrefs

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and an input interface $\opn{commit}\left( c,\mathcal{D} \right)$ (meant to observe the map-agreement sub-algorithm), where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item[-] Safety: (S1), for any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before; (S2), for any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$, if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
%    \item If $c$ was announced by $p$, then eventually a dependency set is suggested for $c$ to $p$.
    \item[-] Liveness: (L1) If a suggestion $\opn{suggest}_p\left( c \right)$ was made, then eventually a suggestion $\opn{suggest}\left( c,\mathcal{D} \right)_p$ is made, and (L2), if a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{commit}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{itemize}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item[-] Safety: (S3), for any decision $\opn{commit}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time; (S4), for any two decisions $\opn{commit}_p\left( c, \mathcal{D}_1 \right)$, $\opn{commit}_q\left( c, \mathcal{D}_2 \right)$, $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.  
    \item[-] Liveness: (L3) if a proposal $propose_p\left( c,\mathcal{D} \right)$ is made, then eventually a decision $\opn{commit}_p\left( c, \mathcal{D} \right)$ is made.
\end{enumerate}

@@

A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $c_1 \preceq_g c_2$ iff there is a path from $c_1$ to $c_2$ and none from $c_2$ to $c_1$.
For example, consider $h$ where $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. 
We have that $\preceq_h = \aset{\left( c_1,c_3 \right)}$.
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every $c_1,c_2\in V\left( g \right)$, $c_1 \preceq_g c_2$ implies $c_1 \ll c_2$, and if $c_1$ and $c_2$ belong to the same strongly connected component $\mathcal{D}$ and $ c_1 <_{\mathcal{D}} c_2$ hold, then $c_1 \ll c_2$. For example, assuming that $c_2 \leq_{\aset{c_1,c_2}} c_1$, the linearizations of $h$ are $\aseq{c_2,c_1,c_3,c_4}$, $\aseq{c_2,c_1,c_4,c_3}$, $\aseq{c_2,c_4,c_1,c_3}$, and $\aseq{c_4,c_2,c_1,c_3}$.

>>>>

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and an input interface $\opn{commit}\left( c,\mathcal{D} \right)$ (meant to observe the map-agreement sub-algorithm), where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item[-] Safety: (\setword{S1}{dep-valid}), for any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before; (\setword{S2}{suggestion-agreement}), for any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$, if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
%    \item If $c$ was announced by $p$, then eventually a dependency set is suggested for $c$ to $p$.
    \item[-] Liveness: (\setword{L1}{eventual-suggestion}) If a suggestion $\opn{suggest}_p\left( c \right)$ was made, then eventually a suggestion $\opn{suggest}\left( c,\mathcal{D} \right)_p$ is made, and (\setword{L2}{re-suggest}), if a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{commit}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{itemize}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item[-] Safety: (\setword{S3}{commit-validity}), for any commit $\opn{commit}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time; (\setword{S4}{commit-agreement}), for any two decisions $\opn{commit}_p\left( c, \mathcal{D}_1 \right)$, $\opn{commit}_q\left( c, \mathcal{D}_2 \right)$, $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.  
    \item[-] Liveness: (\setword{L3}{eventual-commit}) if a proposal $propose_p\left( c,\mathcal{D} \right)$ is made, then eventually a decision $\opn{commit}_p\left( c, \mathcal{D} \right)$ is made.
\end{enumerate}

@@

A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $c_1 \preceq_g c_2$ iff there is a path from $c_2$ to $c_1$ and none from $c_1$ to $c_2$.
For example, consider $h$ where $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. 
We have that $\preceq_h = \aset{\left( c_3,c_1 \right)}$.
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every $c_1,c_2\in V\left( g \right)$, $c_1 \preceq_g c_2$ implies $c_1 \ll c_2$, and if $c_1$ and $c_2$ belong to the same strongly connected component $\mathcal{D}$ and $ c_1 <_{\mathcal{D}} c_2$ hold, then $c_1 \ll c_2$. For example, assuming that $c_1 <_{\aset{c_1,c_2}} c_2$, the linearizations of $h$ are $\aseq{c_3,c_1,c_2,c_4}$, $\aseq{c_3,c_1,c_4,c_2}$, $\aseq{c_3,c_4,c_1,c_2}$,
$\aseq{c_4,c_3,c_1,c_2}$.
